Two-Dimensional Vesicle Hydrodynamics from Hydrophobic Attraction Potential

### 2022-02-11 doc/main_jfm.tex
Peter working on revision

\ReviewerOne{Table~\ref{table2} provides the results of stretching moduli $K_A$ and permeabilities $P$ for various cases. The default setup is shown in the first row. The next two rows show the results for the cases where the length scale related parameters are decreased by 5$\%$ and 10$\%$. One can observe that the constant $K_A$ increases 
and $P$ decreases as size of particles decreases. 
The last two rows demonstrate the results when the force related parameters $\gamma$ and $M$ are adjusted by 5$\%$ and 10$\%$. The quantities examined for these two cases show that $K_A$ increases and $P$ remains constant as inter-particle interaction strength increases. As expected by the fact that the permeability is dependent of the particle size where the gap between each adjacent JP pair is controlled by the size of JP particles. However, the detailed correlation between all model parameters will be explored as 
a direction of future work.}

>>>>

\ReviewerOne{Table~\ref{table2} provides the results of stretching moduli $K_A$ and permeabilities $P$ for various cases. The default setup is shown in the first row. The next two rows show the results for the cases where the length scale related parameters are decreased by 5$\%$ and 10$\%$. One can observe that the constant $K_A$ increases 
and $P$ decreases as size of particles decreases. 
The last two rows demonstrate the results when the force related parameters $\gamma$ and $M$ are adjusted by 5$\%$ and 10$\%$. The quantities examined for these two cases show that $K_A$ increases and $P$ remains constant as inter-particle interaction strength increases. As expected by the fact that the permeability is dependent of the particle size where the gap between each adjacent JP pair is controlled by the size of JP. However, the detailed correlation between all model parameters will be explored as 
a direction of future work.}
